FoRTE baseline

### 2019-04-30 analysis/paper/paper.Rmd
[paper] Add parameter table (and remove trailing whitespace)

@@

@@

>>>>

CRUNCEP met.

@@

| Parameter_name          | Description                                          | Unit                          |
|-------------------------|------------------------------------------------------|-------------------------------|
| `c2n_fineroot`          | C:N ratio in fine roots                              | unitless (mass ratio)         |
| `c2n_leaf`              | C:N ratio in leaves                                  | unitless (mass ratio)         |
| `f_labile`              | Fraction of litter that goes to labile (fast) C pool | unitless (0-1)                |
| `fineroot2leaf` / `q`   | Ratio of fine root to leaf biomass                   | unitless (mass ratio)         |
| `growth_resp_factor`    | Fraction of daily C gain lost to growth respiration  | unitless (0-1)                |
| `leaf_width`            | Mean leaf width (for boundary layer conductance)     | m                             |
| `mort2`                 | C balance ratio at which mortality rapidly increases | unitless (mass ratio)         |
| `nonlocal_dispersal`    | "Proportion of dispersal that is global"             | unitless (0-1)                |
| `quantum_efficiency`    | Farquhar model parameter (TODO)                      | mol CO~2~ (mol photons)^-1^   |
| `r_fract`               | Fraction of C storage to seed reproduction           | unitless                      |
| `root_respiration_rate` | Root respiration rate at reference soil temperature  | μmol CO~2~ (kg fine root)^-1^ |
| `root_turnover_rate`    | Rate of fine rootloss                                | year^-1^                      |
| `SLA`                   | Specific leaf area                                   | m^2^ kg^-1^ C                 |
| `seedling_mortality`    | Proportion of seed that dies and goes to litter pool | unitless (0-1)                |
| `stomatal_slope`        | Slope between _A_ and stomatal conductance (Leuning) | unitless                      |
| `Vcmax`                 | Maximum rate of CO~2~ carboxylation at 15 °C         | μmol m^-2^ s^-1^              |
| `Vm_low_temp`           | Minimum temperature for photosynthesis               | °C                            |
| `water_conductance`     | "Water availability factor"                          | m^-2^ a^-1^ (kg C root)^-1^   |

Table: Parameter descriptions

@@

`r mdcap(param_dist_cap)`
